Cultural Transmission and the Social Contexts of Technological Transitions during the Late Paleolithic of Korea

### 2023-02-24 analysis/paper/paper.qmd
added acknowledgements

<!-- The following line inserts a page break  -->

>>>>

We would like to thank Yongjoon Chang, Seonsook Park, Jaeyoung Kim, Soonmi Lee, Taeyoung Kim, and the staff in Korean national museums, and Sangtaek Lim, Chuntaek Seong, Sangmin Cha, Sooa Kim, Gigil Lee, Myeongjin Choi, and Chanho Park in local archaeological institutions and university museums in Korea for permitting access to their collection used in this study and assisting our trip to Korea. We thank the Quaternary Research Center, Department of Anthropology and Center for Statistics and the Social Sciences at the University of Washington for supporting our research trip. We also appreciate Ben Fitzhugh and Peter Lape for their insightful comments that have greatly improved this manuscript.
